Deep learning approaches on musical assisted-orchestration: an evaluation study

### 2020-05-01 paper/latex/paper.tex
Add to experiments section

@@

We tested our models using 15 targets for orchestration. These targets are not made from combinations of the input data, and some are not even recordings of instruments. Among the targets are recordings of bells, a car horn, a gong, and an environmental recording of a boat docking. By passing these samples into a model, an orchestration of the target is created from the TinySOL samples that were used to train the network.

>>>>

We did not train our model to classify the dynamics of a sample despite TinySOL having pp, mf, and ff recordings for each sample. If we had, then each class would have only one data point. Instead, when the model is used for orchestration, the dynamic is determined by the probability of that sample as output by the model. If the model output a probability higher than $0.66$ for a sample, the ff version of the sample was used. If it was between $0.33$ and $0.66$, then the mf version, and if less than $0.33$ the pp dynamic.

@@

We tested our models using 15 targets for orchestration. Two of the targets were made from TinySOL samples, but the rest are not combinations of input data, and some are not even recordings of instruments. Among the targets are recordings of bells, a car horn, a gong, and a recording of a boat docking. By passing these samples into a model, an orchestration of the target is created from the TinySOL samples that were used to train the network. For orchestrating these targets, we used both the CNN and ResNet models, each trained on combinations of 10 instruments from a possible 10 instruments. The CNN was trained for 49 epochs and the ResNet for 24.

We evaluated our orchestrations both qualitatively and quantitatively. Qualitative inspection was done through an acoustic inspection of the solution, paying close attention to timbre and pitch. For targets that had harmonic content, it was noted if the partials present in the target were also represented in the orchestrated solution. For example, one of the samples of a bell had partials that represented a C sharp minor chord. The ResNet . For a target that contained specific notes, the solution from ResNet contained both the note in the target and its partials: a sample that was two octaves higher, the fifth an octave up, and a minor third two octaves up (mix\_ObA4\_BnC3).
